Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-04-06 paper.tex
New version with fixed tables
Removed superfluous files
Description of special cases

\begin{table}
\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
\label{tab:all_editors_no_fs}}
\centering{}%
%{\scriptsize
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & Corr. coeffic  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.890 $\pm$ 0.09 & 214.365 $\pm$ 22.96 & 634.229 $\pm$ 307.76 & 37.457 $\pm$ 3.12 & 48.324 $\pm$ 25.16 & 18.845 $\pm$ 0.61\\
\hline
K-NN & 0.787 $\pm$ 0.08 & 272.294 $\pm$ 32.38 & 840.594 $\pm$ 240.11 & 47.475 $\pm$ 3.39 & 63.072 $\pm$ 10.29 & 0.001 $\pm$ 0.01\\
\hline 
Random Forest & 0.840 $\pm$ 0.05 & 253.365 $\pm$ 29.43 & 788.937 $\pm$ 282.01 & 44.164 $\pm$ 2.76 & 57.766 $\pm$ 8.15 & 4.906 $\pm$ 0.12\\
\hline 
Linear Regression & 0.872 $\pm$ 0.07 & 308.679 $\pm$ 25.44 & 680.905 $\pm$ 226.41 & 54.053 $\pm$ 4.38 & 52.130 $\pm$ 18.29 & 984.687 $\pm$ 128.21\\
\hline 
SVM & 0.876 $\pm$ 0.04 & 248.763 $\pm$ 27.49 & 732.641 $\pm$ 260.56 & 43.371 $\pm$ 2.35 & 53.471 $\pm$ 6.29 & 6169.239 $\pm$ 281.49\\
\hline 
\end{tabular}
%}
\end{table}

@@

% RELIEFATTRIBUTEEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.892 $\pm$0.102 & 211.147 $\pm$22.41 & 616.347 $\pm$321.254 & 36.928 $\pm$3.414 & 47.299 $\pm$26.827 & 0.4906 $\pm$0.0223\\
\hline 
K-NN & 0.869 $\pm$0.087 & 231.782 $\pm$24.246 & 668.028 $\pm$205.135 & 40.483 $\pm$3.058 & 51.276 $\pm$16.807 & 0.0015 $\pm$0.0042\\
\hline 
Random Forest & 0.91 $\pm$0.048 & 198.16 $\pm$19.499 & 589.353 $\pm$195.801 & 34.61 $\pm$2.27 & 44.209 $\pm$11.634 & 3.633 $\pm$0.2039\\
\hline 
Linear Regression & 0.864 $\pm$0.081 & 346.875 $\pm$25.395 & 695.897 $\pm$242.49 & 60.754 $\pm$4.549 & 53.164 $\pm$19.432 & 0.0124 $\pm$0.0072\\
\hline 
SVM & 0.842 $\pm$0.039 & 252.868 $\pm$33.384 & 858.26 $\pm$318.225 & 44.012 $\pm$3.038 & 62.22 $\pm$7.148 & 38.9667 $\pm$5.7518\\
\hline 
\end{tabular}

% CFSSUBEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.873 $\pm$0.09 & 266.777 $\pm$23.117 & 662.319 $\pm$245.272 & 46.66 $\pm$3.247 & 50.9 $\pm$20.35 & 0.4103 $\pm$0.0428\\
\hline 
K-NN & 0.84 $\pm$0.099 & 289.092 $\pm$22.834 & 743.917 $\pm$260.45 & 50.591 $\pm$3.496 & 57.301 $\pm$22.899 & 0.001 $\pm$0.0006\\
\hline 
Random Forest & 0.85 $\pm$0.106 & 278.417 $\pm$23.073 & 714.134 $\pm$278.654 & 48.713 $\pm$3.434 & 55.264 $\pm$24.412 & 2.479 $\pm$0.1264\\
\hline 
Linear Regression & 0.859 $\pm$0.062 & 356.35 $\pm$22.43 & 708.056 $\pm$195.145 & 62.423 $\pm$4.216 & 53.974 $\pm$14.053 & 0.0067 $\pm$0.0009\\
\hline 
SVM & 0.86 $\pm$0.063 & 288.474 $\pm$30.322 & 817.562 $\pm$253.237 & 50.302 $\pm$2.375 & 60.266 $\pm$5.675 & 32.7252 $\pm$5.7438\\
\hline
\end{tabular}\\

% SOM
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{SOM}}\\
\hline
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 0.866 $\pm$0.104 & 234.091 $\pm$23.186 & 699.563 $\pm$317.196 & 40.924 $\pm$3.248 & 53.698 $\pm$26.867 & 0.4754 $\pm$0.1228\\
\hline 
K-NN & 0.868 $\pm$0.086 & 237.91 $\pm$25.344 & 665.639 $\pm$212.05 & 41.547 $\pm$3.141 & 50.96 $\pm$16.721 & 0.0009 $\pm$0.0035\\
\hline 
Random Forest & 0.898 $\pm$0.051 & 211.867 $\pm$20.072 & 617.776 $\pm$187.155 & 37.017 $\pm$2.461 & 46.581 $\pm$11.144 & 2.932 $\pm$0.1083\\
\hline 
Linear Regression & 0.855 $\pm$0.075 & 351.993 $\pm$23.72 & 714.756 $\pm$214.213 & 61.65 $\pm$4.278 & 54.665 $\pm$16.881 & 0.0113 $\pm$0.0074\\
\hline 
SVM & 0.845 $\pm$0.035 & 267.706 $\pm$33.819 & 888.331 $\pm$308.932 & 46.604 $\pm$2.865 & 64.62 $\pm$5.445 & 32.2689 $\pm$4.7404\\
\hline 
\end{tabular}

\end{table}

@@

***TO DO ***: better describe (number of instances) and justify the special cases (why we have chosen them).

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 0.889 $\pm$0.074 & 71.258 $\pm$21.291 & 125.19 $\pm$50.085 & 39.251 $\pm$11.769 & 47.495 $\pm$15.933 & 0.046 $\pm$0.0278\tabularnewline
\hline 
K-NN & 0.826 $\pm$0.1 & 87.602 $\pm$23.206 & 158.629 $\pm$54.164 & 47.621 $\pm$10.32 & 59.168 $\pm$14.428 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
Random Forest & 0.871 $\pm$0.082 & 74.634 $\pm$22.166 & 139.743 $\pm$54.357 & 40.618 $\pm$10.214 & 52.219 $\pm$16.267 & 0.1069 $\pm$0.0053\tabularnewline
\hline 
Linear Regression & 0.838 $\pm$0.089 & 97.513 $\pm$18.874 & 155.273 $\pm$45.562 & 54.172 $\pm$13.598 & 60.314 $\pm$21.168 & 0.0069 $\pm$0.0012\tabularnewline
\hline 
SVM & 0.874 $\pm$0.066 & 78.743 $\pm$22.254 & 147.295 $\pm$57.99 & 42.428 $\pm$7.826 & 53.286 $\pm$9.351 & 0.0598 $\pm$0.0157\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 0.775 $\pm$0.15 & 573.405 $\pm$192.219 & 860.313 $\pm$456.217 & 58.26 $\pm$15.867 & 65.997 $\pm$29.447 & 0.0238 $\pm$0.0018\tabularnewline
\hline 
K-NN & 0.732 $\pm$0.163 & 596.615 $\pm$205.368 & 933.058 $\pm$356.108 & 60.619 $\pm$17.854 & 71.363 $\pm$22.336 & 0 $\pm$0.0002\tabularnewline
\hline 
Random Forest & 0.867 $\pm$0.073 & 449.161 $\pm$127.796 & 671.758 $\pm$212.739 & 45.575 $\pm$9.8 & 51.372 $\pm$11.159 & 0.0606 $\pm$0.005\tabularnewline
\hline 
Linear Regression & 0.733 $\pm$0.195 & 680.157 $\pm$263.788 & 1103.971 $\pm$850.685 & 69.775 $\pm$27.238 & 86.106 $\pm$71.316 & 0.0024 $\pm$0.0005\tabularnewline
\hline 
SVM & 0.804 $\pm$0.122 & 529.349 $\pm$172.496 & 846.013 $\pm$341.117 & 53.26 $\pm$11.915 & 63.539 $\pm$18.247 & 0.029 $\pm$0.0151\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 0.9 $\pm$0.098 & 670.244 $\pm$181.047 & 1065.337 $\pm$413.835 & 40.833 $\pm$10.858 & 43.561 $\pm$19.866 & 0.0302 $\pm$0.0016\tabularnewline
\hline 
K-NN & 0.733 $\pm$0.192 & 1057.212 $\pm$385.036 & 1875.849 $\pm$916.958 & 61.879 $\pm$12.366 & 68.747 $\pm$15.978 & 0 $\pm$0.0001\tabularnewline
\hline 
Random Forest & 0.876 $\pm$0.108 & 771.825 $\pm$326.339 & 1490.492 $\pm$930.576 & 45.399 $\pm$14.137 & 55.912 $\pm$31.703 & 0.0777 $\pm$0.0041\tabularnewline
\hline 
Linear Regression & 0.863 $\pm$0.118 & 922.334 $\pm$289.01 & 1399.844 $\pm$619.623 & 56.107 $\pm$16.171 & 56.425 $\pm$25.091 & 0.0045 $\pm$0.0006\tabularnewline
\hline 
SVM & 0.867 $\pm$0.1 & 873.222 $\pm$345.164 & 1621.478 $\pm$985.241 & 50.847 $\pm$11.83 & 57.232 $\pm$20.404 & 0.0423 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 0.832 $\pm$0.24 & 14.179 $\pm$6.615 & 23.82 $\pm$11.86 & 43.405 $\pm$20.387 & 55.787 $\pm$30.474 & 0.0089 $\pm$0.0016\tabularnewline
\hline 
K-NN & 0.793 $\pm$0.236 & 15.34 $\pm$8.706 & 26.571 $\pm$16.635 & 46.2 $\pm$23.768 & 60.09 $\pm$35.205 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
Random Forest & 0.858 $\pm$0.172 & 14.185 $\pm$6.692 & 23.569 $\pm$11.831 & 42.534 $\pm$16.799 & 53.295 $\pm$23.408 & 0.0321 $\pm$0.0044\tabularnewline
\hline 
Linear Regression & 0.821 $\pm$0.252 & 14.62 $\pm$7.917 & 24.793 $\pm$15.076 & 44.573 $\pm$24.265 & 56.854 $\pm$35.071 & 0.0019 $\pm$0.0005\tabularnewline
\hline 
SVM & 0.835 $\pm$0.21 & 14.01 $\pm$7.608 & 25.612 $\pm$15.297 & 40.663 $\pm$16.026 & 53.276 $\pm$18.45 & 0.0198 $\pm$0.0146\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\caption{Predicting Total sales for Editor704 (ReliefFAttributeEval-FS) }

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 0.893 $\pm$0.075 & 69.699 $\pm$19.853 & 122.48 $\pm$47.284 & 38.486 $\pm$11.531 & 46.677 $\pm$16.018 & 0.0275 $\pm$0.003\tabularnewline
\hline 
K-NN & 0.856 $\pm$0.101 & 78.393 $\pm$24.118 & 147.075 $\pm$58.023 & 42.577 $\pm$10.988 & 54.416 $\pm$15.542 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
Random Forest & 0.877 $\pm$0.079 & 73.134 $\pm$22.949 & 137.604 $\pm$56.143 & 39.785 $\pm$10.689 & 51.348 $\pm$16.98 & 0.1282 $\pm$0.0137\tabularnewline
\hline 
Linear Regression & 0.873 $\pm$0.06 & 89.719 $\pm$18.306 & 140.653 $\pm$47.12 & 49.452 $\pm$10.495 & 53.196 $\pm$14.156 & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM & 0.877 $\pm$0.069 & 77.301 $\pm$22.249 & 146.462 $\pm$57.679 & 41.665 $\pm$7.994 & 53.098 $\pm$9.505 & 0.045 $\pm$0.0159\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\caption{Predicting Total sales for Editor704 (CfsSubsetEval-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & Corr. coefficient  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 0.801 $\pm$0.092 & 104.874 $\pm$21.376 & 174.571 $\pm$47.332 & 58.111 $\pm$14.731 & 67.577 $\pm$22.612 & 0.0178 $\pm$0.0028\tabularnewline
\hline 
K-NN & 0.782 $\pm$0.116 & 99.45 $\pm$24.305 & 170.827 $\pm$46.342 & 54.529 $\pm$12.277 & 65.864 $\pm$18.338 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
Random Forest & 0.776 $\pm$0.128 & 101.933 $\pm$23.664 & 180.557 $\pm$51.203 & 56.098 $\pm$13.624 & 69.862 $\pm$23.274 & 0.0738 $\pm$0.003\tabularnewline
\hline 
Linear Regression & 0.801 $\pm$0.096 & 106.617 $\pm$21.523 & 173.179 $\pm$46.584 & 59.109 $\pm$14.958 & 67.527 $\pm$24.529 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 0.818 $\pm$0.075 & 94.285 $\pm$25.516 & 180.536 $\pm$62.67 & 50.792 $\pm$8.477 & 65.624 $\pm$6.245 & 0.0382 $\pm$0.0183\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\caption{Predicting Total sales for Editor704 (SOM-FS)}

>>>>

\begin{table}
\caption{Predicting Total sales for all editors (all the features). 30 repetitions, 10-fold cross validation.
\label{tab:all_editors_no_fs}}
\centering{}%
%{\scriptsize
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 89.0 $\pm$ 0.09  & 214.37 $\pm$ 22.96  & 634.23 $\pm$ 307.76  & 37.46 $\pm$ 3.12  & 48.32 $\pm$ 25.16  & 18.85 $\pm$ 0.61\tabularnewline
\hline 
K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  & 0.001 $\pm$ 0.01\tabularnewline
\hline 
RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
\hline 
LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
\hline 
SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}%}
%}
\end{table}

@@

% RELIEFATTRIBUTEEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{ReliefAttributeEval}}\\
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 89.2 $\pm$0.10 & 211.15 $\pm$22.41 & 616.35 $\pm$321.25 & 36.93 $\pm$3.41 & 47.30 $\pm$26.83 & 0.49 $\pm$0.02\\
\hline 
K-NN & 86.9 $\pm$0.09 & 231.78 $\pm$24.25 & 668.03 $\pm$205.14 & 40.48 $\pm$3.06 & 51.28 $\pm$16.81 & 0.002 $\pm$0.004\\
\hline 
RF & 91.0 $\pm$0.05 & 198.16 $\pm$19.50 & 589.35 $\pm$195.80 & 34.61 $\pm$2.27 & 44.21 $\pm$11.63 & 3.63 $\pm$0.20\\
\hline 
LR & 86.4 $\pm$0.08 & 346.88 $\pm$25.40 & 695.90 $\pm$242.49 & 60.75 $\pm$4.55 & 53.16 $\pm$19.43 & 0.01 $\pm$0.01\\
\hline 
SVM & 84.2 $\pm$0.04 & 252.87 $\pm$33.38 & 858.26 $\pm$318.23 & 44.01 $\pm$3.04 & 62.22 $\pm$7.15 & 38.97 $\pm$5.75\\
\hline 
\end{tabular}

% CFSSUBEVAL
\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
\multicolumn{7}{|c|}{\textit{CfsSubEval}}\\
\hline
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\\
\hline 
M5P & 87.0 $\pm$0.09 & 266.78 $\pm$23.12 & 662.32 $\pm$245.27 & 46.66 $\pm$3.25 & 50.9 $\pm$20.35 & 0.41 $\pm$0.04\\
\hline 
K-NN & 84.0 $\pm$0.10 & 289.09 $\pm$22.83 & 743.92 $\pm$260.45 & 50.59 $\pm$3.50 & 57.30 $\pm$22.90 & 0.001 $\pm$0.001\\
\hline 
RF & 85.0 $\pm$0.11 & 278.42 $\pm$23.07 & 714.13 $\pm$278.65 & 48.71 $\pm$3.43 & 55.26 $\pm$24.41 & 2.48 $\pm$0.13\\
\hline 
LR & 85.9 $\pm$0.06 & 356.35 $\pm$22.43 & 708.06 $\pm$195.15 & 62.42 $\pm$4.22 & 53.97 $\pm$14.05 & 0.01 $\pm$0.001\\
\hline 
SVM & 86.0 $\pm$0.06 & 288.47 $\pm$30.32 & 817.56 $\pm$253.24 & 50.30 $\pm$2.38 & 60.27 $\pm$5.68 & 32.73 $\pm$5.74\\
\hline
\end{tabular}\\

% SOM
\centering{}% SOM
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
\multicolumn{7}{|c|}{\textit{SOM}}\tabularnewline
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 86.6 $\pm$0.10  & 234.09 $\pm$23.19  & 699.56 $\pm$317.20  & 40.92 $\pm$3.25  & 53.70 $\pm$26.87  & 0.475 $\pm$0.12\tabularnewline
\hline 
K-NN  & 86.8 $\pm$0.09  & 237.91 $\pm$25.34  & 665.64 $\pm$212.05  & 41.55 $\pm$3.14  & 50.96 $\pm$16.72  & 0.001 $\pm$0.004\tabularnewline
\hline 
RF & 89.8 $\pm$0.05  & 211.87 $\pm$20.07  & 617.78 $\pm$187.16  & 37.02 $\pm$2.46  & 46.58 $\pm$11.14  & 2.93 $\pm$0.11\tabularnewline
\hline 
LR  & 85.5 $\pm$0.08  & 351.99 $\pm$23.72  & 714.76 $\pm$214.21  & 61.65 $\pm$4.28  & 54.67 $\pm$16.88  & 0.01 $\pm$0.01\tabularnewline
\hline 
SVM  & 84.5 $\pm$0.04  & 267.71 $\pm$33.82  & 888.33 $\pm$308.93  & 46.60 $\pm$2.87  & 64.62 $\pm$5.45  & 32.27 $\pm$4.74\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

***TO DO ***: Justify the special cases (why we have chosen them).

Table XX shows the details of each of these editorials.

\begin{table}
\caption{Description of editorials considered as special cases.
\label{tab:desc_editorials}}
\centering{}%
\begin{tabular}{|r|l|l|l|}
\hline 
 & Different books sold & Total copies sold & Description\\
\hline 
\textit{All editorials} & 6083 & 3201645 & 209 editorials\\
\hline 
\textit{UDL704} & 293 & 58236 & Editorial with most different\\ 
       &     &       & books sold\\
\hline 
\textit{UDLU11} & 180 & 249481 & Editorial with medium number\\ 
       &     &       &  of different books sold\\
\hline 
\textit{UDL929} & 216 & 460752 & Best selling editorial\\
\hline 
\textit{UDLW12} & 97 & 2635 & Medium selling editorial\\
\hline 
\end{tabular}
\end{table}

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for Editor704 (ReliefFAttributeEval-FS) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 89.3 $\pm$0.08  & 69.70 $\pm$19.85  & 122.48 $\pm$47.28  & 38.49 $\pm$11.53  & 46.68 $\pm$16.02 & 0.028 $\pm$0.003\tabularnewline
\hline 
K-NN  & 85.6 $\pm$0.10  & 78.39 $\pm$24.12  & 147.07 $\pm$58.02  & 42.58 $\pm$10.99  & 54.42 $\pm$15.54  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.7 $\pm$0.08  & 73.13 $\pm$22.95  & 137.60 $\pm$56.14  & 39.79 $\pm$10.69  & 51.35 $\pm$17.00  & 0.13 $\pm$0.01\tabularnewline
\hline 
LR  & 87.3 $\pm$0.06  & 89.72 $\pm$18.31  & 140.65 $\pm$47.12  & 49.45 $\pm$10.50  & 53.20 $\pm$14.16  & 0.0008 $\pm$0.0005\tabularnewline
\hline 
SVM  & 87.7 $\pm$0.07  & 77.30 $\pm$22.25  & 146.46 $\pm$57.68  & 41.67 $\pm$7.99  & 53.10 $\pm$9.51  & 0.05 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for Editor704 (CfsSubsetEval-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 80.1 $\pm$0.09 & 104.87 $\pm$21.38 & 174.57 $\pm$47.33 & 58.11 $\pm$14.73 & 67.58 $\pm$22.61 & 0.018 $\pm$0.003\tabularnewline
\hline 
K-NN & 78.2 $\pm$0.12 & 99.45 $\pm$24.31 & 170.83 $\pm$46.34 & 54.53 $\pm$12.28 & 65.86 $\pm$18.34 & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 77.6 $\pm$0.13 & 101.93 $\pm$23.66 & 180.56 $\pm$51.20 & 56.10 $\pm$13.62 & 69.86 $\pm$23.27 & 0.0738 $\pm$0.003\tabularnewline
\hline 
LR & 80.1 $\pm$0.10 & 106.62 $\pm$21.52 & 173.18 $\pm$46.58 & 59.11 $\pm$14.96 & 67.53 $\pm$24.53 & 0.0004 $\pm$0.0005\tabularnewline
\hline 
SVM & 81.8 $\pm$0.08 & 94.29 $\pm$25.52 & 180.54 $\pm$62.67 & 50.79 $\pm$8.48 & 65.62 $\pm$6.25 & 0.040 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[!ht]
\caption{Predicting Total sales for Editor704 (SOM-FS)}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE & RMSE & RAE (\%) & RRSE (\%) & Time (s)\tabularnewline
\hline 
\hline 
M5P & 89.2 $\pm$0.07 & 71.536 $\pm$18.95 & 123.06 $\pm$42.13 & 39.43 $\pm$10.58 & 47.20 $\pm$15.16 & 0.031 $\pm$0.007\tabularnewline
\hline 
K-NN & 85.8 $\pm$0.09 & 79.42 $\pm$21.47 & 140.95 $\pm$44.93 & 43.34 $\pm$10.07 & 53.31 $\pm$14.37 & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 87.7 $\pm$0.08 & 73.98 $\pm$20.91 & 134.11 $\pm$51.70 & 40.48 $\pm$10.51 & 50.41 $\pm$16.38 & 0.10 $\pm$0.0076\tabularnewline
\hline 
LR & 87.5 $\pm$0.06 & 88.70 $\pm$16.34 & 135.03 $\pm$35.18 & 49.08 $\pm$10.47 & 51.97 $\pm$13.65 & 0.0006 $\pm$0.0005\tabularnewline
\hline 
SVM & 87.8 $\pm$0.06 & 81.09 $\pm$22.48 & 154.82 $\pm$59.93 & 43.65 $\pm$7.36 & 55.72 $\pm$7.15 & 0.031 $\pm$0.003\tabularnewline
\hline 
\end{tabular}
\end{table}
